---
title: "BBN Global Seaweed"
author: "Iona Campbell"
date: "15/04/2021"
output:
   prettydoc::html_pretty:
    theme: HYPSTR
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(prettydoc)
```
\
\
\

## Proposed Methods for BBN: From KAP survey, literature and expert opinion
\

### Suggested flow chart of method 1
```{r}
library(DiagrammeR)
grViz("digraph flowchart {
      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']

      # edge definitions with the node IDs
      tab1 -> tab3;
      tab2 -> tab3;
      tab3 -> tab4 -> tab5 -> tab6
      }

      [1]: '1a. HACCP to draft farm system' 
      [2]: '1b. Root Cause Analysis to draft farm system'
      [3]: '2. Match variables from literature and questionnaire with nodes in the system'
      [4]: '3. Use data from literature and questionnaire to build CPT tables for each node'
      [5]: '4. Define the conceptual model with risk to productivity as outcome'
      [6]: '5. Validate model with panel of experts'
      ")
```
\
\

## Data Wrangling for Network Comparison between Philippines and Tanzania
   
1. Re-structure data away from KAP scores and list each survey question as a variable (catagorical ordered)
2. Make two data-sets, so that we can explore a comparison between a network from Philippines and Tanzania
3. Plot a correlation graph for each dataset: qgraph() function in qgraph)
   + Find out which variables are positively correlated
   + Note which ones aren't correlated 


